Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-10-15 doc/JFLA2022/paper.tex
fix typo in conclusion

\Hydras wants to be provide a connection between scientific literature (\emph{e.g.},~\cite{KP82, KS81, schutte}) and proof assistant technology. For the mathematician, it may give a concrete view of the mathematical content, not only through full proofs, but also through significative computations: examples, functions associated with constructive proofs, etc. For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. %It may be also used as a library, through opam packages.
It is also a medium sized library (more than 50,000 LOC), dependent on various tools and libraries of the \coq ecosystem, which  may be also used to experiment new techniques of continuous maintenance of the code and its documentation.

>>>>

\Hydras wants to provide a connection between scientific literature (\emph{e.g.},~\cite{KP82, KS81, schutte}) and proof assistant technology. For the mathematician, it can give a concrete view of the mathematical content, not only through full proofs, but also through illuminating computations: examples, functions associated with constructive proofs, etc. For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. %It may be also used as a library, through opam packages.
It is also a medium sized library (more than 50,000 LOC), dependent on various tools and libraries of the \coq ecosystem, which  may be also used to experiment new techniques of continuous maintenance of the code and its documentation.
